---
title: "STAT3613 Marketing Engineering Project"
output: 
  pdf_document: 
  fig_height: 7
  fig_width: 6
editor_options: 
  chunk_output_type: console
---
```{r initialization and data import, message=FALSE, warning=FALSE}
library(psych)
library(ggplot2)
library(reshape2)
library(Hmisc)
library(smacof)
library(ca)

par(mfrow=c(1,1))
options(scipen=100,digits=4)

data=read.csv(file='../data/survey.csv',header=T)
data=data[-49,]

bg=data[2:6] # backgrounds
pref=data[16:27] # three most preferred canteens
res=data[28:35] # reason


```

#Q7 Preference
```{r}
head(pref)
colnames(pref)
# set others = 4
pref[is.na(pref)]=4
head(pref)

#type="ordinal" orginal transformation
fit<-unfolding(pref,ndim=2,type="ordinal")
fit
#summary(fit)

plot(fit,cex=2,main="",ylim=c(-1,1),xlim=c(-1,1))
#row and column coordinates
#fit$conf.row # subjects
#fit$conf.col # objects

#fit$confdist
#pref[5,]

```

## Conclusion
1. Maxim is the most popular canteen, followed by Swire.
2. Few people like SU
3. Starbucks, India, USweet, Cafe330 and Delifrance are competitors (foreign flavors)

#Q8 Reasons
```{r}
head(res)
CtName=character()
CtAttr=character()
for (i in 1:52){
  for (j in 1:3){
        lengthj=length(colnames(pref)[which(pref[i,]==j)])
        if (lengthj!=0){
          for (n in 1:lengthj){
            for (k in 1:8){
              if (j%in%strsplit(as.character(res[i,k]),", ")[[1]]){
              CtName=c(CtName,colnames(pref)[which(pref[i,]==j)][n])
              CtAttr=c(CtAttr,colnames(res)[k])
              }
            }
          }
         } 
  }
}

dfres=data.frame(CtName,CtAttr)
head(dfres,30)
dim(dfres[which(dfres$CtName=='BIJAS'),])
tb=table(dfres$CtAttr,dfres$CtName)
tb

fit<-ca(tb)
summary(fit)
cacoord(fit,type="principal",dim=1:2)
par(mar=c(4,4,1,1))
plot(fit)

```


## Conclusion

1. Two dimensions explain almost 70% percent, quite well.

### For attributes
2. Dimension 1: primary contributor is Environment, secondary contributor is Quantity. Can be explained as Quantity v.s. Environment.Account for 45.1% +20.1%=65.6% of dimension 1.
3. Dimension 2:  primary contributor is Display, secondary contributor is Efficiency. Can be explained as Display v.s. Efficiency. Account for 33.9% +28.6%=62.5% of dimension 2.
4. Fitness: the quality values range from a high of 92.4 to a low of 9.2%. Only Taste, Location and Others have quality values less than 50%.


### For canteens
5. Dimension 1: Starbucks and BIJAS contribute to over 62%. Dimension 1 can be explained as (Starbucks and BIJAS) vs Others.
6. Dimension 2: 5 canteens contribute over average (8.3%). Dimension 2 can be explained as (Cafe330, Delifrance, India) v.s. (Maxim and Udeli), i.e., foreign style food v.s. Hong Kong style food.

### From perceptual graph
7. Group 1: Starbucks, BIJAS. High efficiency and good environment, but expensive and not enough quantity.
8. Group 2: Delifrance, Cafe330, iBakery. Good food display, but not efficient and location not convenient. .
9. Group 3: USweet, SU, India. Good quantity, but inadequate environment and efficiency.
10. Group 4: Maxim, Subway, Swire. Convenient location, good taste and economic price but inadequate environment.
11. India canteen is isolated, so is UDeli.

